% header 
\chapter{Todo articles}

\section{From binder:}
2: frameworks, techniques and metrics.\\
3: automated new analysis.\\
4: same as 14. \\
5:\\
7: Techniques, noun scheme, named entities \\
8: Techniques, algorithms, Key Phrase Extraction Algorithm(KEA).\\
9: Maybe the text mining aspects of it. \\
11: More for the width to understand the topic. \\
12: Language models for financial news recommendations. \\
13: About the impact of Negative words. \\
14: Predict direction of a market stock. \\
15: text mining approaches. \\
16: text classification\\
18: wc, TM, expected returns, tactical asses allocation. \\
19: Textual analysis of stock market prediction using financial news articles. \\
20: same as 10.\\
22: Forecasting intra-day stock price trends with text mining techniques.\\
23: Techniques and applications for sentiment analysis. \\
24: Set of articles about sentiment. \\
25: More text mining and such. \\

\section{Links}
\url{http://en.wikipedia.org/wiki/Sentiment_analysis}\\
\url{https://developers.google.com/prediction/docs/sentiment_analysis}\\
\url{http://www.slideshare.net/mcjenkins/how-sentiment-analysis-works}\\
\url{http://sentimentsymposium.com/}\\
\url{http://www.sentiment140.com/}\\
\url{http://www.cs.cornell.edu/people/pabo/research.html}\\
\url{http://www.cs.cornell.edu/home/llee/papers.html}\\
\url{http://www.cs.cornell.edu/home/llee/}\\
\url{http://cacm.acm.org/magazines/2013/4/162501-techniques-and-applications-for-sentiment-analysis/fulltext}\\
\url{http://text-processing.com/demo/sentiment/}\\
\url{http://www.forexsentiment.net/}\\
\url{http://cs.stanford.edu/people/alecmgo/papers/TwitterDistantSupervision09.pdf}\\
\url{http://people.cs.pitt.edu/~wiebe/pubs/papers/emnlp05polarity.pdf}\\


