\chapter{Data and System}
The data. What used, how and why. Acquired data how and from where. 

System specification and solutions. 

\section{Tweet structure}
There are a lot of meta data in the tweets. In fact most of the data in a tweet
object is not the tweet content itself. 

\section{What data was used}
\section{How to Obtain the tweets}
Simple guide to access the twitter api:  http://datascienceandprogramming.wordpress.com/2013/05/14/twitter-api/

\section{What's the Structure of the data}
\section{Problems and shortcomings}

\section{Dictionaries}\label{sec:dict}

Tim Loughran and Bill McDonald has a set of dictionaries available from the
websites of University of Notre Dame \footnote{fiks tekst: nd.edu:
\url{http://www3.nd.edu/~mcdonald/Word_Lists.html}}. 

List of Dictionaries:
\begin{itemize}
    \item negative words
General list of negative words. No particular category. Used for basic   
    \item positive words
This dictionary contains a small set of positive words. There are no general
category for the words. The words are not directly related to finance. 
    \item Uncertainty words
    \item litigious words
    \item modal words strong
    \item modal words weak
\end{itemize}

%Dictionary expansion. 
There are a lot of words that are not classified yet. Those words should be
stored and classified later. This to improve the classifiers potential to
correctly classify tweets.  

\section{System specifications}
Description of the system designed and implemented. 

Three main phases: data retrieval, sentiment classification, trend calculation
and comparison. 

\subsection{Architecture}
Top level design of how the software works and communicates through the layers. 
\subsection{Technology}
The technology used, frameworks etc. 

Python, javascript. 
Twython, Flask, angularjs, d3. 

\subsection{Frameworks} 
Jeg har sett litt på for å se om de kan være brukbare. 

\paragraph{Twython (python bassert)}
Rameverk for tilkobling og integrasjon mot twitter apiet. 
Se https://github.com/ryanmcgrath/twython/tree/master/examples for eksempler. 
https://github.com/ryanmcgrath/twython

\paragraph{Flask (python bassert)}
Minimalt rammeverk for webapplikasjoner. Dette gjør det enkelt å lage et API som
leverer ferdir klassifiserte tweets og tidssegmenter. 
http://flask.pocoo.org/

\paragraph{AngularJS}
Generelt godt rammeverk for frontend på web. Kan kanskje brukes sammen med d3
for å presentere dataene. 
http://angularjs.org/

\paragraph{D3}
Javascript rammeverk bassert på data. 
Skal visst være bra å bruke til å tegne grafer og slikt
Jeg tenker at det kan være gunstig i presentasojnen av data og sammenlinkningene
av moving average og den kalkulerte twitter trenden. 
http://d3js.org/

\subsection{Structure}
code structure and which files are where. 
\subsection{Environment}
how the system is run and under which conditions.
\subsection{Issues}
Problems in the implementation and the general solution. 


